---
title: '1'
author: "Rodion Sharafiev"
date: "10 01 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
setwd("C:\\Users\\rsharafiev\\DS\\exam\\Acea-Smart-Water-Analytics")
library(lubridate)
library(data.table)
library(aTSA)
library(vars)
df <- read.csv("Lake_Bilancino.csv")
```


Our features are Rainfall_S_Piero, Rainfall_Mangona, Rainfall_S_Agata, Rainfall_Cavallina, Rainfall_Le_Croci, Temperature_Le_Croci.
Output Lake_Level and Flow_Rate.


```{r }
df$п.їDate = strptime(df$п.їDate, "%d/%m/%Y")
df$Date <- ymd(df$п.їDate)
```
#Some checks for data

Is date ordered and there are no any missing days?
```{r}
df <- df[order(df$Date), ]
df['Interval']=df$Date - shift(df$Date, n=1, fill=NA, type="lag")
days <- df$Interval

for(i in days)
{
  
  if(isTRUE(i > 1) || is.null(i))
  {
    print(i)
  }
    
}
df<-df[,2:10]
```
Yes. Also we will save only our date.

Let's see sum summaries.
```{r }

summary(df)
summary(df[1:578,])
```
We see that first 578 records have are useless for us (no data about rainfall, temperature and missing values for flow rate).
So we don't need them any more.
```{r }
df <- df[579:6603,]
summary(df)
```
Let's check stationary and make some transformations.
```{r}
ts_Flow_Rate <- ts(df$Flow_Rate, start=c(2004,2), frequency = 365.25)
plot(ts_Flow_Rate)
adf.test(ts_Flow_Rate)
ts_Flow_Rate <- log(ts(df$Flow_Rate+1, start=c(2004,2), frequency = 365.25))
plot(ts_Flow_Rate)
adf.test(ts_Flow_Rate)
```
```{r}
ts_Lake_Level <- ts(df$Lake_Level, start=c(2004,2), frequency = 365.25)
plot(ts_Lake_Level)
adf.test(ts_Lake_Level)
ts_Lake_Level<-log10(ts_Lake_Level)
plot(ts_Lake_Level)
adf.test(ts_Lake_Level)
```
```{r}
ts_Rainfall_S_Piero <- ts(df$Rainfall_S_Piero, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_S_Piero)
result = adf.test(ts_Rainfall_S_Piero)

```
```{r}
ts_Rainfall_Mangona <- ts(df$Rainfall_Mangona, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_Mangona)
result = adf.test(ts_Rainfall_Mangona)

```
```{r}
ts_Rainfall_S_Agata <- ts(df$Rainfall_S_Agata, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_S_Agata)

```
```{r}
ts_Rainfall_Cavallina <- ts(df$Rainfall_Cavallina, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_Cavallina)
result = adf.test(ts_Rainfall_Cavallina)

```
```{r}
ts_Rainfall_Le_Croci <- ts(df$Rainfall_Le_Croci, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_Le_Croci)
result = adf.test(ts_Rainfall_Le_Croci)

```
```{r}
ts_Temperature_Le_Croci <- ts(df$Temperature_Le_Croci, start=c(2004,2), frequency = 365.25)
plot(ts_Temperature_Le_Croci)
result = adf.test(ts_Temperature_Le_Croci)

```

```{r}
y_1 <- cbind(ts_Flow_Rate, ts_Lake_Level)
colnames(y_1)<-cbind("Flow_Rate", "Lake_Level")

x_1 <- cbind(ts_Rainfall_Cavallina, ts_Rainfall_Le_Croci, ts_Rainfall_Mangona, ts_Rainfall_S_Agata, ts_Rainfall_S_Piero, ts_Temperature_Le_Croci, shift(ts_Rainfall_Cavallina), shift(ts_Rainfall_Le_Croci), shift(ts_Rainfall_Mangona), shift(ts_Rainfall_S_Agata), shift(ts_Rainfall_S_Piero),shift(ts_Temperature_Le_Croci),shift(ts_Rainfall_Cavallina, n=2L), shift(ts_Rainfall_Le_Croci, n=2L), shift(ts_Rainfall_Mangona, n=2L), shift(ts_Rainfall_S_Agata, n=2L), shift(ts_Rainfall_S_Piero, n=2L),shift(ts_Temperature_Le_Croci, n=2L))
colnames(x_1)<-cbind("Rainfall_Cavallina", "Rainfall_Le_Croci", "Rainfall_Mangona", "Rainfall_S_Agata", "Rainfall_S_Piero", "Temperature_Le_Croci","Rainfall_Cavallina_1", "Rainfall_Le_Croci_1", "Rainfall_Mangona_1", "Rainfall_S_Agata_1", "Rainfall_S_Piero_1","Temperature_Le_Croci_1","Rainfall_Cavallina_2", "Rainfall_Le_Croci_2", "Rainfall_Mangona_2", "Rainfall_S_Agata_2", "Rainfall_S_Piero_2","Temperature_Le_Croci_2")

lagselect <- VARselect(y=y_1, type = "const", exogen = x_1)
lagselect$selection
```
Now p is 6.

Let's try to predict values.
```{r}
border <- length(y_1[,1])-2-2*365
train_y <- y_1[3:border,]
train_x <- x_1[3:border,]
test_y <- y_1[(border+1):6023,]
test_x <- x_1[(border+1):6023,]


```

```{r}
Model4 <- VAR(train_y, p = 6, type = "const",  exogen = train_x)
summary(Model4)
```
P-value, R-squared and F-static are good.
```{r}
pred_y <- predict(Model4, n.ahead =2*365, dumvar=test_x, ci=0.95)
```




Visualize test data and prediction.
```{r}

plot(y_1)
plot(pred_y)
```

```{r}
cross_val_3 <- function(x, y, p) {
  max <- length(y[,1])-2
  border <- max-2*365
  pred_length <- 3
  errors_Flow=0
  errors_Level=0
  measures = 0
  while (border+pred_length <= max) {
    train_y <- y[3:border,]
    train_x <- x[3:border,]
    test_y <- y[(border+1):(border+pred_length),]
    test_x <- x[(border+1):(border+pred_length),]
    test_Model <- VAR(train_y, p = p, type = "const",  exogen = train_x)
    pred_y <- predict(test_Model, n.ahead = pred_length, dumvar=test_x, ci=0.95)
    check<-pred_y$fcst$Flow_Rate
    errors_Flow <- sum((check[,1]-test_y[,1])^2)+errors_Flow
    check<-pred_y$fcst$Lake_Level
    errors_Level <- sum((check[,1]-test_y[,2])^2)+errors_Level
    measures=measures + 3
    border=border+pred_length
  }
  RMSE_Flow = sqrt(errors_Flow/measures)
  RMSE_Level = sqrt(errors_Level/measures)
  c(RMSE_Flow,RMSE_Level)
}
```

```{r}
cross_val_4 <- function(x, y, p) {
  max <- length(y[,1])-2
  border <- max-2*365
  pred_length <- 3
  errors_Flow=0
  errors_Level=0
  measures = 0
  while (border+pred_length <= max) {
    train_y <- y[3:border,]
    train_x <- x[3:border,]
    test_y <- y[(border+1):(border+pred_length),]
    test_x <- x[(border+1):(border+pred_length),]
    test_Model <- VAR(train_y, p = p, type = "const",  exogen = train_x)
    pred_y <- predict(test_Model, n.ahead = pred_length, dumvar=test_x, ci=0.95)
    check<-pred_y$fcst$Flow_Rate
    errors_Flow <- sum((exp(check[,1])-exp(test_y[,1]))^2)+errors_Flow
    check<-pred_y$fcst$Lake_Level
    errors_Level <- sum((10^check[,1]-10^test_y[,2])^2)+errors_Level
    measures=measures + 3
    border=border+pred_length
  }
  RMSE_Flow = sqrt(errors_Flow/measures)
  RMSE_Level = sqrt(errors_Level/measures)
  c(RMSE_Flow,RMSE_Level)
}
```

```{r}
p=6
cross_val_3(x_1,y_1,p)
```

```{r}
cross_val_4(x_1,y_1,p)
```