---
title: "acea_water_petrigano"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Aquifer
## Petrignano
### Data preparation
```{r}
df <- as.data.frame(read.table('./acea-water-prediction/Aquifer_Petrignano.csv', header = TRUE, sep=','))
head(df, n=20)
```


Remove NA elements from data 
```{r}
df <- df[complete.cases(df$Rainfall_Bastia_Umbra),]
rownames(df) <- 1:nrow(df)
```
```{r}
df <- subset(df, select = -c(Depth_to_Groundwater_P25, Temperature_Petrignano ))
colnames(df) <- c("Date", "Rainfall", "Depth_to_Groundwater","Temperature", " Volume", " Hydrometry" )
head(df, n=20)
```

Plot data
```{r, message=FALSE}
library('ggplot2')
library('forecast')
library('zoo')
library('dplyr')
library('data.table')
library('imputeTS')
library('xts')
library('tseries')
library('stats')
library('nlme')
library('fpp')
library('lubridate')
library('TSstudio')
library('AICcmodavg')
```

### Data preparation
```{r}
# sort by date
df$Date <- as.Date(df$Date, format= "%d/%m/%Y")
df <- df[order(df$Date), ]
interval = df$Date - shift(df$Date, n=1, fill=NA, type="lag")
```
```{r}
for(i in interval)
{
  
  if(isTRUE(i > 1) || is.null(i))
  {
    print(i)
  }
    
}
```

As we can see, there are some missing values that we need to fix. We can see it from stat and from graphics where red places or outliers.

```{r}
# find that there are some missing values in data set
ggplot_na_distribution(df$Depth_to_Groundwater)
ggplot_na_distribution(df$Rainfall)
ggplot_na_distribution(df$Temperature)
ggplot_na_distribution(df$` Volume`)
ggplot_na_distribution(df$` Hydrometry`)
statsNA(df$Depth_to_Groundwater)
statsNA(df$Rainfall)
statsNA(df$Temperature)
statsNA(df$` Volume`)
statsNA(df$` Hydrometry`)
```

So we need to fix data

# Interpolate data to fix missing values
```{r}
times_dd <- ts(df$Depth_to_Groundwater, start = df$Date[1], frequency=1)
ggplot_na_distribution(times_dd)
times_dd <- na_interpolation(times_dd, option="spline")
```

After interpolation

```{r}
ggplot_na_distribution(times_dd)
plot( times_dd,xlab = "Time", ylab = "Depth_to_Groundwater", main="Depth", axes=FALSE, type="l")
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

Volume has some troubles
```{r}
df$` Volume` <- ifelse(df$` Volume` == 0, NaN, df$` Volume`)
times_vv <- ts(df$` Volume`, start = df$Date[1], frequency=1)
ggplot_na_distribution(times_vv)
times_vv <- na_interpolation(times_vv, option="linear")
ggplot_na_distribution(times_vv)
plot( times_vv,xlab = "Time", ylab = "Volume", main="Volume", axes=FALSE, type="l")
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

Interpolation can't be realised due to there are no missing values, there are only 0 values, that are anomaly for for current data. So we can change 0 to nan and then interpolate
```{r}
df$` Hydrometry` <- ifelse(df$` Hydrometry` == 0, NaN, df$` Hydrometry`)
times_hh <- ts(df$` Hydrometry`, start = df$Date[1], frequency=1)
ggplot_na_distribution(times_hh)
times_hh <- na_interpolation(times_hh, option="linear")
ggplot_na_distribution(times_hh)
plot( times_hh,xlab = "Time", ylab = "Hydrometry", main="Hydrometry", axes=FALSE, type="l")
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

### Resampling
the series can be assembled unevenly over time and to eliminate this resampling is used
So if data was collected once an hour, and then suddenly once a day, and then once every 3 hours we will make it at equal intervals. But there we haven't got any troubles that was checd by counting interval higher

### try to unsderstand in what way and frequency it will be more efficient to predict
```{r}
times_dd <- ts(df$Depth_to_Groundwater, start = df$Date[1], frequency=1)
times_dd <- na_interpolation(times_dd, option="spline")
time_dd_week <- period.apply(as.xts(times_dd), endpoints(as.xts(times_dd), "weeks"), range)
times_dd <- na_interpolation(time_dd_week, option="spline")
plot( time_dd_week,xlab = "Time", ylab = "Depth_to_Groundwater", main="Depth", axes=FALSE, type="l")
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

```{r}
times_t <- ts(df$Temperature, start = df$Date[1], frequency=1)
times_tt_week <- period.apply(as.xts(times_t), endpoints(as.xts(times_t), "weeks"), range)
plot( times_tt_week,xlab = "Time", ylab = "Temperature", main="Temperature", axes=FALSE, type="l")
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

```{r}
times_vv <- ts(df$` Volume`, start = df$Date[1], frequency=1)
times_vv_week <- period.apply(as.xts(times_vv), endpoints(as.xts(times_vv), "weeks"), range)
times_vv_week <- na_interpolation(times_vv_week, option="linear")
plot( times_vv_week,xlab = "Time", ylab = "Volume", main="Volume", axes=FALSE, type="l")
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

```{r}
times_hh <- ts(df$` Hydrometry`, start = df$Date[1], frequency=1)
times_hh_week <- period.apply(as.xts(times_hh), endpoints(as.xts(times_hh), "weeks"), range)
times_hh_week <- na_interpolation(times_hh_week, option="linear")
plot( times_hh_week,xlab = "Time", ylab = "Hydrometry", main="Hydrometry", axes=FALSE, type="l")
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

```{r}
times <- ts(df$Rainfall, start = df$Date[1], frequency=1)
times_week <- period.apply(as.xts(times), endpoints(as.xts(times), "weeks"), range)
plot( times_week,xlab = "Time", ylab = "Rainfall", main="Rainfall", axes=FALSE)
axis(1,at=seq(df$Date[1], df$Date[length(df$Date)], by="years"),labels=unique(as.character(df$Date, format= "%Y")))
axis(2)
box()
```

We can say that it is not obvious to resample data, we can make predictions for one day and it will be quite accurate and full. If we will take for day or month we can lose some info that will be critical for people' life. Also there is no such big outliers that require smoothing


# Analyse data 
```{r}
#depth <- diff(depth)

depth <- na_interpolation(df$Depth_to_Groundwater, option = "linear")
depth_ts <- ts(depth, start = df$Date[1], frequency=365)
```

look at seasonal, because we can make some decisions from the seasonalty.
```{r}
ts_seasonal(ts(na_interpolation(df$Depth_to_Groundwater, option = "linear"), start = df$Date[1], frequency=12), type = "all")
ts_plot(depth_ts)
```


```{r}
rainfall <- na_interpolation(df$Rainfall, option = "linear")
rainfall_ts <- ts(rainfall, start = df$Date[1], frequency=12)
rainfall_ts <- diff(rainfall_ts)
ts_seasonal(rainfall_ts, type = "all")
```

Rainfall ???

```{r}
temperature <- na_interpolation(df$Temperature, option = "linear")
temperature_ts <- ts(temperature, start = df$Date[1], frequency=12)
temperature_ts <- diff(temperature_ts)
ts_seasonal(temperature_ts, type = "all")
```

From the plot we can see that the maximum temperature was in August, minimum in December

```{r}
volume <- na_interpolation(df$` Volume`, option = "linear")
volume_ts <- ts(volume, start = df$Date[1], frequency=12)
volume_ts <- diff(volume_ts)
ts_seasonal(volume_ts, type = "all")
```

Maximum volume was in March, minimum in December

```{r}
hydrometry <- na_interpolation(df$` Hydrometry`, option = "linear")
hydrometry_ts <- ts(hydrometry, start = df$Date[1], frequency=12)
hydrometry_ts <- diff(hydrometry_ts)
ts_seasonal(hydrometry_ts, type = "all")
```

Maximum in August, minimum in January.

The volume and hydrometry reached their minimum around the same time
