---
title: "Lake Bilancio"
author: "Rodion Sharafiev"
date: "08 01 2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



```{r}
setwd("C:\\Users\\rsharafiev\\DS\\exam\\Acea-Smart-Water-Analytics")
library(lubridate)
library(ggplot2)
library(imputeTS)
library(data.table)
library(tseries)
library(urca)
library(aTSA)
library(TSstudio)
library(forecast)
library(vars)
df <- read.csv("Lake_Bilancino.csv")
```


Our features are Rainfall_S_Piero, Rainfall_Mangona, Rainfall_S_Agata, Rainfall_Cavallina, Rainfall_Le_Croci, Temperature_Le_Croci.
Output Lake_Level and Flow_Rate.


```{r }
df$п.їDate = strptime(df$п.їDate, "%d/%m/%Y")
df$Date <- ymd(df$п.їDate)
```
#Some checks for data

Is date ordered and there are no any missing days?
```{r}
df <- df[order(df$Date), ]
df['Interval']=df$Date - shift(df$Date, n=1, fill=NA, type="lag")
days <- df$Interval

for(i in days)
{
  
  if(isTRUE(i > 1) || is.null(i))
  {
    print(i)
  }
    
}
df<-df[,2:10]
```
Yes. Also we will save only our date.

Let's see sum summaries.
```{r }

summary(df)
summary(df[1:578,])
```
We see that first 578 records have are useless for us (no data about rainfall, temperature and missing values for flow rate).
So we don't need them any more.
```{r }
df <- df[579:6603,]
summary(df)
```
Let's check stationary and make some transformations.
```{r}
ts_Flow_Rate <- ts(df$Flow_Rate, start=c(2004,2), frequency = 365.25)
plot(ts_Flow_Rate)
adf.test(ts_Flow_Rate)
ts_Flow_Rate <- log(ts(df$Flow_Rate+1, start=c(2004,2), frequency = 365.25))
plot(ts_Flow_Rate)
adf.test(ts_Flow_Rate)
```
```{r}
ts_Lake_Level <- ts(df$Lake_Level, start=c(2004,2), frequency = 365.25)
plot(ts_Lake_Level)
adf.test(ts_Lake_Level)
ts_Lake_Level<-log10(ts_Lake_Level)
plot(ts_Lake_Level)
adf.test(ts_Lake_Level)
```
```{r}
ts_Rainfall_S_Piero <- ts(df$Rainfall_S_Piero, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_S_Piero)
result = adf.test(ts_Rainfall_S_Piero)

```
```{r}
ts_Rainfall_Mangona <- ts(df$Rainfall_Mangona, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_Mangona)
result = adf.test(ts_Rainfall_Mangona)

```
```{r}
ts_Rainfall_S_Agata <- ts(df$Rainfall_S_Agata, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_S_Agata)

```
```{r}
ts_Rainfall_Cavallina <- ts(df$Rainfall_Cavallina, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_Cavallina)
result = adf.test(ts_Rainfall_Cavallina)

```
```{r}
ts_Rainfall_Le_Croci <- ts(df$Rainfall_Le_Croci, start=c(2004,2), frequency = 365.25)
plot(ts_Rainfall_Le_Croci)
result = adf.test(ts_Rainfall_Le_Croci)

```
```{r}
ts_Temperature_Le_Croci <- ts(df$Temperature_Le_Croci, start=c(2004,2), frequency = 365.25)
plot(ts_Temperature_Le_Croci)
result = adf.test(ts_Temperature_Le_Croci)

```

Now we need to determine p.
```{r}
y <- cbind(ts_Flow_Rate, ts_Lake_Level)
colnames(y)<-cbind("Flow_Rate", "Lake_Level")
y[1,2]=0
x <- cbind(ts_Rainfall_Cavallina, ts_Rainfall_Le_Croci, ts_Rainfall_Mangona, ts_Rainfall_S_Agata, ts_Rainfall_S_Piero, ts_Temperature_Le_Croci)
colnames(x)<-cbind("Rainfall_Cavallina", "Rainfall_Le_Croci", "Rainfall_Mangona", "Rainfall_S_Agata", "Rainfall_S_Piero", "Temperature_Le_Croci")
lagselect <- VARselect(y=y, type = "const", exogen = x)
lagselect$selection
```
We will use AIC's p=5.
Prepare some train and test data.
```{r}
train_y <- y[1:4000,]
train_x <- x[1:4000,]
test_y <- y[4001:6025,]
test_x <- x[4001:6025,]
```

Create model with p=5.
```{r}
Model1 <- VAR(train_y, p = 5, type = "const",  exogen = train_x)
summary(Model1)
```
P-value, R-squared and F-static are good.

Let's try to predict values.
```{r}
pred_y <- predict(Model1, n.ahead =2025, dumvar=test_x, ci=0.95)

```

Visualize test data and prediction.
```{r}

plot(y)
plot(pred_y)
```
Let's compare and calculate mistakes.
```{r}

check<-pred_y$fcst$Flow_Rate
plot(check[,1]~test_y[,1])
errors <- abs(check[,1]-test_y[,1])
summary(errors)

```
It can be better... OK, try something new later.
```{r}
check<-pred_y$fcst$Lake_Level
plot(check[,1]~test_y[,2])
errors <- abs(check[,1]-test_y[,2])
summary(errors)
```
Closer to x=y line. But can be better... Also try it later.
